### 2011-02-21 trunk/deliverables/D2_2_Ontology/fast_d2_2_3_ontology.tex
improved ontology UML diagram
git-svn-id: https://svn.forge.morfeo-project.org/fast-fp7project@1275 d8b0c59b-6544-0410-94d9-83a5658a058e

\begin{itemize}
	\item Section~\ref{sub:classes_instances_and_templates} has been significantly extended with a more in-depth discussion of prototype theory, and a first proposal for prototype-based semantics for RDF, as they are employed in FAST.
	\item A section for the \emph{VocDoc} tool, which was developed in part for generating online and PDF documentation for the FAST ontology, has been added as App.~\ref{sec:vocdoc}.
	\item The ontology itself has remained more or less stable since D2.2.2.~\cite{moeller2010fast_ontology}. However, a handful of small changes and corrections have been performed, e.g., to reflect the terminology changes in the prototype section (\emph{prototype} instead of \emph{template}, \emph{clone} instead of \emph{copy}).
	\item The document as a whole has been revised, and minor changes (mostly, spelling, grammar and small updates to reflect latest developments) have been throughout the deliverable.
	\item The online documentation of the FAST Gadget ontology at \url{http://purl.oclc.org/fast/ontology/gadget} has been updated to reflect the changes in this version of the deliverable.
\end{itemize}

@@

Regarding the layering from the actual gadget down to the embedded Web services, the central classes in the conceptual model of FAST can be grouped into three levels: the gadget and screen flow level at the top, the level of individual screens in the middle, and the level of Web services at the bottom. This layering is reflected in Fig.~\ref{fig:uml_composition}, which illustrates the central compositional relationships of the model. As the figure shows, a \emph{gadget} in FAST is mainly composed of a \emph{screen flow}, which it wraps. The \emph{screen flow} is composed of one or more \emph{screens}, which is turn comprises the three \emph{screen components} of the visual front-end (the \emph{form}), the back end service (the \emph{resource}) and the data \emph{operator}. Finally, \emph{forms} are assembled from \emph{form elements}, while \emph{resources} wrap \emph{backend services}.

>>>>

\begin{itemize}
	\item Section~\ref{sub:classes_instances_and_templates} has been significantly extended with a more in-depth discussion of prototype theory, and a first proposal for prototype-based semantics for RDF, as they are employed in FAST.
	\item A section for the \emph{VocDoc} tool, which was developed in part for generating online and PDF documentation for the FAST ontology, has been added as App.~\ref{sec:vocdoc}.
	\item The ontology itself has remained more or less stable since D2.2.2.~\cite{moeller2010fast_ontology}. However, a handful of small changes and corrections have been performed, e.g., to reflect the terminology changes in the prototype section (\emph{prototype} instead of \emph{template}, \emph{clone} instead of \emph{copy}).
	\item Based on comments from the previous review, Fig.~\ref{fig:ontology_uml} has been corrected and improved with a legend.
	\item The document as a whole has been revised, and minor changes (mostly, spelling, grammar and small updates to reflect latest developments) have been throughout the deliverable.
	\item The online documentation of the FAST Gadget ontology at \url{http://purl.oclc.org/fast/ontology/gadget} has been updated to reflect the changes in this version of the deliverable.
\end{itemize}

@@

Regarding the layering from the actual gadget down to the embedded Web services, the central classes in the conceptual model of FAST can be grouped into three levels: the gadget and screen flow level at the top, the level of individual screens in the middle, and the level of Web services at the bottom. This layering is reflected in Fig.~\ref{fig:uml_composition}, which illustrates the central compositional relationships of the model. As the figure shows, a \emph{gadget} in FAST is mainly composed of a \emph{screen flow}, which it wraps. The \emph{screen flow} is composed of one or more \emph{screens}, which in turn comprises the three \emph{screen components} of the visual front-end (the \emph{form}), the back end service (the \emph{resource}) and the data \emph{operator}. Finally, \emph{forms} are assembled from \emph{form elements}, while \emph{resources} wrap \emph{backend services}.
